Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-16 paper.tex
fuel cycle edits

\subsection{The Fuel Cycle}
This work aims to assess the impact of the operational uncertainties of a simple
transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel.  The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with \glspl{MOX}, consisting of plutonium blended with natural
uranium.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}
    \label{fig:power}
\end{figure}

The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
used fuel.  At first , it is sourced only from \glspl{UOX}, then used MOX fuel
as it becomes available for reprocessing.

Both fuel reprocessing and fabrication are done at a constant rate (constrained
by the feed materials availabilities).  The enrichment of the UOX is processed
on demand.  Buffer storages (not shown on Figure \ref{fig:cycle}) is present
between all facilities with constant processing rates.

In this works, a time step of 1 month have been considered, i.e. each output
metrics are reported one each month and decay process have not be taking into
account.

>>>>

\subsection{The Fuel Cycle}
This work aims to assess the impact of the operational uncertainties of a simple
transition, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
transition starts around year 35, with the deployment of \glspl{FBR}. The \glspl{FBR} are loaded
with \gls{MOX}, which consists of plutonium blended with natural
uranium.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with the full production,
        the \glspl{LWR} contribution, the \glspl{FBR} labelled in blue, orange, and green, respectively.}
    \label{fig:power}
\end{figure}

The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
as it becomes available for reprocessing.

Both fuel reprocessing and fabrication are done at a constant rate (constrained
by the feed material availability).  The enrichment of the \gls{UOX} is processed
on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) is present
between all facilities with constant processing rates.

In this work, a time step of 1 month has been considered, i.e., each output
metric is reported once per month. Additionally, decay processes have not be taken into
account.
